PAMELA: an annotation-based Java Modeling Framework

### 2021-02-16 implementation.tex
Antoine's changes

\begin{itemize}
    \vspace{-0.2cm}\item Core implementation (\texttt{pamela-core}) provides all base features for PAMELA. It contains 20k lines of code involving 184 classes. This code is covered with unit test (6k lines of code, 112 classes). Reached code coverage is about 66\%.
    \vspace{-0.2cm}\item \texttt{pamela-security-patterns} is an add-on library containing some security-pattern implementations.
    \vspace{-0.2cm}\item \texttt{pamela-perf-tests} contains benchmarking tools whose purpose is to quantifiate PAMELA performances. 
\end{itemize}

>>>>

\begin{itemize}
    \vspace{-0.2cm}\item Core implementation (\texttt{pamela-core}) provides all base features for PAMELA. It contains 20k lines of code involving 184 classes. This code is covered with unit tests (6k lines of code, 112 classes). Reached code coverage is about 66\%.
    \vspace{-0.2cm}\item \texttt{pamela-security-patterns} is an add-on library containing some security-pattern implementations.
    \vspace{-0.2cm}\item \texttt{pamela-perf-tests} contains benchmarking tools whose purpose is to quantify PAMELA performances. 
\end{itemize}

### 2021-02-16 pamelaProcess.tex
Antoine's changes

\sg{
Here are various conceivable scenarios for PAMELA use:
\begin{itemize}
    \vspace{-0.2cm}\item \textbf{Programming use} : programmers reuse existing annotations and write model and code at the same time (the modelers and programmers share the same artifacts : the Java code). This scenario includes the case where the model (made by the modelers) is pre-existing.
    \vspace{-0.2cm}\item \textbf{Reengineering} : programmers start from an existing base of code (legacy) and refactor it while replacing existing code by abstract method declarations in Java interface, reducing risks of errors.
    \vspace{-0.2cm}\item \textbf{Aspect-oriented programming} : programmers may use or redefine "patterns" (eg Security Patterns \cite{silva20}) which offers code weaving at runtime, as well as runtime monitoring.
    \vspace{-0.2cm}\item \textbf{Advanced programmers use} : programmers may extends PAMELA with their own annotations, their own implementations, their own patterns, etc...
\end{itemize}
}

>>>>

\sg{
Here are various conceivable scenarios for PAMELA use:
\begin{itemize}
    \vspace{-0.2cm}\item \textbf{Programming use} : programmers reuse existing annotations and write model and code at the same time (the modelers and programmers share the same artifacts : the Java code). This scenario includes the case where the model (made by the modelers) is pre-existing.
    \vspace{-0.2cm}\item \textbf{Reengineering} : programmers start from an existing base of code (legacy) and refactor it while replacing this code by abstract method declarations in Java interface, reducing risks of errors.
    \vspace{-0.2cm}\item \textbf{Aspect-oriented programming} : programmers may use or redefine "patterns" (e.g., Security Patterns \cite{silva20}) which offers code weaving at runtime, and runtime monitoring.
    \vspace{-0.2cm}\item \textbf{Advanced programmers use} : programmers may extend PAMELA with their own annotations, implementations or patterns.
\end{itemize}
}
